\section{Designing a Betting Algorithm: Coin Betting Potentials}
\label{section:coin-betting-potentials}

%In this section, we will provide a framework to analyze betting algorithms.

For sequential betting on i.i.d. coin flips, an optimal strategy has been
proposed by \citet{Kelly-1956}.  The strategy assumes that the coin flips
$\{g_t\}_{t=1}^\infty$, $g_t \in \{+1,-1\}$, are generated i.i.d. with known
probability of heads. If $p \in [0,1]$ is the probability of heads, the Kelly
bet is to bet $\beta_t = 2p - 1$ at each round. He showed that, in the long
run, this strategy will provide more wealth than betting any other fixed
fraction of the current wealth~\cite{Kelly-1956}.

For adversarial coins, Kelly betting does not make sense. With perfect
knowledge of the future, the gambler could always bet everything on the right
outcome.  Hence, after $T$ rounds from an initial endowment $\epsilon$, the
maximum wealth he would get is $\epsilon 2^T$.  Instead, assume he bets the
same fraction $\beta$ of its wealth at each round.  Let $\Wealth_t(\beta)$ the
wealth of such strategy after $t$ rounds.  As observed in
\cite{McMahan-Abernethy-2013}, the optimal fixed fraction to bet is
$\beta^*=(\sum_{t=1}^T g_t)/T$ and it gives the wealth
\begin{equation}
\label{eq:opt_wealth}
\Wealth_T(\beta^*)
= \epsilon \exp\left(T \cdot \KL{\tfrac{1}{2}+\tfrac{\sum_{t=1}^T g_t}{2T}}{\tfrac{1}{2}}\right)
\ge \epsilon \exp\left(\tfrac{(\sum_{t=1}^T g_t)^2}{2 T}\right) \; ,
\end{equation}
where the inequality follows from Pinsker's inequality~\citep[Lemma
11.6.1]{Cover-Thomas-2006}.

However, even without knowledge of the future, it is possible to go very close
to the wealth in \eqref{eq:opt_wealth}.  This problem was studied by
\citet{Krichevsky-Trofimov-1981}, who proposed that after seeing the coin flips
$g_1, g_2, \dots, g_{t-1}$ the empirical estimate $k_t = \frac{1/2 +
\sum_{i=1}^{t-1} \indicator[g_i = +1]}{t}$ should be used instead of $p$. Their
estimate is commonly called \emph{KT estimator}.\footnote{Compared to the
maximum likelihood estimate $\frac{\sum_{i=1}^{t-1} \indicator[g_i =
+1]}{t-1}$, KT estimator shrinks slightly towards $\nicefrac{1}{2}$.} The KT
estimator results in the betting
\begin{equation}
\label{equation:kt-estimator-betting-strategy}
\beta_t = 2k_t - 1 = \tfrac{\sum_{i=1}^{t-1} g_i}{t}
\end{equation}
which we call \emph{adaptive Kelly betting based on the KT estimator}. It looks
like an online and slightly biased version of the oracle choice of $\beta^*$.
This strategy guarantees\footnote{See Appendix~\ref{section:logloss-to-wealth}
for a proof. For lack of space, all the appendices are in the supplementary
material.}
\[
\Wealth_T
\ge \tfrac{\Wealth_T(\beta^*)}{2\sqrt{T}}
= \tfrac{\epsilon}{2\sqrt{T}} \exp\left(T \cdot \KL{\tfrac{1}{2}+\tfrac{\sum_{t=1}^T g_t}{2T}}{\tfrac{1}{2}}\right)\; .
\]
This guarantee is optimal up to constant
factors~\citep{Cesa-Bianchi-Lugosi-2006} and mirrors the guarantee of the Kelly
bet.

Here, we propose a new set of definitions that allows to generalize the
strategy of adaptive Kelly betting based on the KT estimator. For these strategies
it will be possible to prove that, for any $g_1, g_2, \dots, g_t \in [-1,1]$,
\vspace{-0.3cm}
\begin{equation}
\label{equation:wealth-lower-bound-generic}
\Wealth_t \ge F_t \left( \sum_{i=1}^t g_i \right) \; ,
\end{equation}
where $F_t(x)$ is a certain function. We call such functions \emph{potentials}.
The betting strategy will be determined uniquely by the potential (see (c) in
the Definition~\ref{definition:potential}), and we restrict our attention to
potentials for which \eqref{equation:wealth-lower-bound-generic} holds. These
constraints are specified in the definition below.
\begin{definition}[Coin Betting Potential]
\label{definition:potential}
Let $\epsilon > 0$. Let $\{F_t\}_{t=0}^\infty$ be a sequence of functions
$F_t:(-a_t, a_t)  \to \R_+$ where $a_t > t$.  The sequence
$\{F_t\}_{t=0}^\infty$ is called a \textbf{sequence of coin betting potentials
for initial endowment $\epsilon$}, if it satisfies the following three
conditions:
\begin{enumerate}[(a)]
\item $F_0(0) = \epsilon$.

\item For every $t \ge 0$, $F_t(x)$ is even, logarithmically convex, strictly
increasing on $[0,a_t)$, and
$\lim_{x \to a_t} F_t(x) = +\infty$.
\item For every $t \ge 1$, every $x \in [-(t-1), (t-1)]$ and every $g \in [-1,1]$, $\left(1 + g \beta_t \right) F_{t-1}(x) \ge F_t(x+g)$, when
\begin{equation}
\label{equation:potential-based-strategy}
\beta_t=\tfrac{F_t(x + 1) - F_t(x - 1)}{F_t(x + 1) + F_t(x - 1)} \;.
\end{equation}
\end{enumerate}
The sequence $\{F_t\}_{t=0}^\infty$ is called a
\textbf{sequence of excellent coin betting potentials for initial
endowment $\epsilon$} if it satisfies conditions (a)--(c) and the condition (d)
below.
\begin{enumerate}[(a)]
\setcounter{enumi}{3}
\item For every $t \ge 0$, $F_t$ is twice-differentiable and
satisfies $x \cdot F_t''(x) \ge F_t'(x)$ for every $x \in [0,a_t)$.
\end{enumerate}
\end{definition}
Let's give some intuition on this definition.  First, let's show by induction
on $t$ that (b) and (c) of the definition together with \eqref{equation:def_wt} give a betting strategy that satisfies
\eqref{equation:wealth-lower-bound-generic}. The base case $t=0$ is trivial. At
time $t \ge 1$, bet $w_t=\beta_t \Wealth_{t-1}$
where $\beta_t$ is defined in \eqref{equation:potential-based-strategy}, then
\begin{align*}
\Wealth_t
&= \Wealth_{t-1} + w_t g_t
= (1+g_t \beta_t) \Wealth_{t-1} \\
&\ge (1 + g_t \beta_t) F_{t-1}(\sum_{i=1}^{t-1} g_i)
\ge F_t(\sum_{i=1}^{t-1} g_i + g_t)
= F_t \left( \sum_{i=1}^t g_i \right) \; .
\end{align*}
%
The formula for the potential-based
strategy~\eqref{equation:potential-based-strategy} might seem strange. However,
it is derived---see Theorem~\ref{theorem:optimal-betting-fraction}
in Appendix~\ref{section:optimal-betting-fraction}---by minimizing the
worst-case value of the right-hand side of the inequality used w.r.t. to $g_t$
in the induction proof above: $F_{t-1}(x) \ge \tfrac{F_{t}(x +
g_t)}{1+g_t\beta_t}$.

The last point, (d), is a technical condition that allows us to seamlessly
reduce OLO over a Hilbert space to the one-dimensional problem, characterizing
the worst case direction for the reward vectors.

Regarding the design of coin betting potentials, we expect any potential that
approximates the best possible wealth in \eqref{eq:opt_wealth} to be a good
candidate.  In fact, $F_t(x)=\epsilon \exp \left(x^2/(2t)\right)/\sqrt{t}$,
essentially the potential used in the parameter-free algorithms in
\cite{McMahan-Orabona-2014, Orabona-2014} for \ac{OLO} and in
\cite{Chaudhuri-Freund-Hsu-2009, Luo-Schapire-2014, Luo-Schapire-2015} for
\ac{LEA}, approximates \eqref{eq:opt_wealth} and it is an excellent coin
betting potential---see Theorem~\ref{thm:exp_x2} in
Appendix~\ref{section:optimal-betting-fraction}. Hence, our framework provides
intuition to previous constructions and in Section~\ref{section:kt-estimator}
we show new examples of coin betting potentials.

In the next two sections, we presents the reductions to effortlessly solve \emph{both} the generic \ac{OLO} case and \ac{LEA} with a betting potential.