%\vspace{-0.1cm}

\section{Preliminaries}
\label{section:preliminaries}

We begin by providing some definitions.
The \ac{KL} divergence between two discrete distributions $p$ and $q$ is
$\KL{p}{q} = \sum_{i} p_i \ln\left( p_i/q_i \right)$. If $p,q$ are real numbers
in $[0,1]$, we denote by $\KL{p}{q} = p \ln \left(p/q \right) + (1-p) \ln
\left((1-p)/(1-q) \right)$ the \ac{KL} divergence between two Bernoulli
distributions with parameters $p$ and $q$.  We denote by $\H$ a Hilbert space
with inner product $\langle \cdot, \cdot\rangle$ and by $\norm{\cdot}$ the
induced norm.  We denote by $\norm{\cdot}_1$ the $1$-norm in $\R^N$.  A
function $F:I \to \R_+$ is called \emph{logarithmically convex} iff $f(x) =
\ln(F(x))$ is convex.  Let $f:V \to \R \cup \{\pm\infty\}$, the Fenchel
conjugate of $f$ is $f^*:V^* \to \R \cup \{\pm \infty\}$ defined on the dual
vector space $V^*$ by $f^*(\theta) = \sup_{x \in V} \ \langle \theta, x \rangle
- f(x)$.  A function $f:V \to \R \cup \{+ \infty\}$ is said to be proper if
$\dom f \neq \emptyset$.  If $f$ is a proper lower semi-continuous convex
function then $f^*$ is also proper lower semi-continuous convex and
$f^{**}=f$.

\textbf{Coin Betting.} We consider a gambler making
repeated bets on the outcomes of adversarial coin flips. The gambler starts with an
initial endowment $\epsilon > 0$. In each round $t$, he bets on the outcome of a
coin flip $g_t \in \{-1,1\}$, where $+1$ denotes heads and $-1$ denotes tails.
We do not make any assumption on how $g_t$ is generated, that is, it can be
chosen by an adversary.

The gambler can bet any amount on either heads or tails. However, he is not
allowed to borrow any additional money. If he loses, he loses the betted
amount; if he wins, he gets the betted amount back and, in addition to that, he
gets the same amount as a reward.  We encode the gambler's bet in round $t$ by a
single number $\beta_t \in [-1,1]$. The sign of $\beta_t$ encodes whether he is
betting on heads or tails. The absolute value encodes the betted amount as the
fraction of his current wealth.

Defining $\Wealth_t$ to be the gambler's wealth at the end of round $t$, it satisfies the
recurrence
\begin{align}
\label{equation:wealth-recurrence}
\Wealth_0 & = \epsilon &
& \text{and} &
\Wealth_t & = (1 + g_t \beta_t) \Wealth_{t-1} \qquad \text{for $t \ge 1$} \; .
\end{align}
Note that since $\beta_t \in [-1,1]$, the gambler's wealth stays always non-negative.
The gambler's net reward (difference of wealth and initial endowment) after $t$
rounds is
\begin{align}
\label{equation:reward-wealth}
\Reward_t = \Wealth_t - \ \epsilon \; .
\end{align}
We generalize the problem slightly by allowing the outcome of the coin flip
$g_t$ to be any real number in the interval $[-1,1]$.  Equations
\eqref{equation:wealth-recurrence} and \eqref{equation:reward-wealth} defining
wealth and reward remain exactly the same.
